TITLE

### 2021-02-25 outputs/Paper.Rmd

library(tidyverse)
#install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")

@@

After discussing data gathering method, we sampled data in R. We totally have **`r size`** observations, and 14 of following features according to the questionnaires.

>>>>

library(tidyverse)
#install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")
library(ggplot2)
library(kableExtra)

@@

After discussing data gathering method, we sampled data in R [@citeR]. We totally have **`r size`** observations, and 14 of following features according to the questionnaires.
